Draft Research pt2

### 2019-03-09 draftResearch_pt2.Rmd
Z-scores computation

>>>>

# Generate rankings
```{r}
z_score_count <- function(df, stat, invert=FALSE) {
  stat <- enquo(stat)
  col_nm <- paste0("z_", quo_name(stat))

  df <- df %>% 
    mutate(s_z = (!! stat - mean(!! stat)) / sd(!! stat))

  if (invert) {
    df %>%
      mutate(s_z = -s_z) -> df
  }

  df %>%
   rename(!! col_nm := s_z)
}

z_score_rate <- function(df, stat, quantity, invert=FALSE) {
  stat <- enquo(stat)
  quantity <- enquo(quantity)
  col_nm <- paste0("z_",quo_name(stat))

  df %>%
    mutate(s_q = (!! stat - mean(!! stat)) * !! quantity) %>%
    mutate(s_z = (s_q - mean(s_q)) / sd(s_q)) -> df

  if (invert) {
    df %>%
      mutate(s_z = -s_z) -> df
  }

  df %>%
    rename(!! col_nm := s_z) %>%
    select(-s_q)
}

(z_pitchers <- pitchers %>%
  z_score_count(SV) %>%
  z_score_count(HLD) %>%
  z_score_rate(ERA, IP, TRUE) %>%
  z_score_count(SO) %>%
  z_score_rate(WHIP, IP, TRUE) %>%
  mutate(
    z_sum = pmap_dbl(
      select(., starts_with("z_")), 
      sum
    )
  ) %>%
  arrange(desc(z_sum))
)

(z_batters <- batters %>%
  z_score_count(H) %>%
  z_score_count(HR) %>%
  z_score_count(R) %>%
  z_score_count(RBI) %>%
  z_score_count(BB) %>%
  z_score_count(SO, TRUE) %>%
  z_score_count(SB) %>%
  z_score_rate(OBP, PA) %>%
  z_score_rate(OPS, PA) %>%
  mutate(
    z_sum = pmap_dbl(
      select(., starts_with("z_")), 
      sum
    )
  ) %>%
  arrange(desc(z_sum))
)

z_batters %>% saveRDS("data/z_batters.Rds")
z_pitchers %>% saveRDS("data/z_pitchers.Rds")

z_batters %>% 
  mutate(type = "Batter") %>%
  bind_rows(z_pitchers) %>%
  select(playerid, Name, type, ADP, z_sum) %>%
  filter(ADP < 999) %>%
  mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
  arrange(z_sum %>% desc()) %>%
  ggplot(aes(x=ADP,y=z_sum,color=type)) +
  geom_point() -> p

plotly::ggplotly(p)

```

### To Do
1. Strategy for projecting scoring stats not in this data set (i.e. CG/SHO, etc)
2. Validate findings, control z-scores between batters and players to make them comparable
3. Develop tiers of players (linear model? nearest neighbor?), visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
4. Replacement level stuff (new section)
